---
output:
  pdf_document: default
bibliography: __template.bib
---


## R Markdown Skeleton

<!-- remotes::install_github("ROpenSci/bibtex")  -->



Citation: [@wu2019pay]


```{r TOP, echo=FALSE, message=FALSE, eval=TRUE, results='hide'}

#### note ``` (3 backticks)
##### R code goes in here.  Set code chunk environment options above


projpath <- getwd()

if(!exists("xdbsock")) {
    xdbsock <- ""
    ## cat("\n", "Parameter 'xdbsock' not found, setting to empty string for general usage", "\n")
}


library(RMySQL)
library(knitr)

drv <- dbDriver("MySQL")


xdbuser <- Sys.getenv("MAS405_AWS_DZES_DB_RO_USER") ### 
xpw     <- Sys.getenv("MAS405_AWS_DZES_DB_RO_PW") ### 
xdbname <- Sys.getenv("MAS405_AWS_DZES_DB_RO_DBNAME") ### 
xdbhost <- Sys.getenv("MAS405_AWS_DZES_DB_RO_HOST") ###
xdbport <- as.integer( Sys.getenv("MAS405_AWS_DZES_DB_RO_PORT") )

con <- dbConnect(drv, user=xdbuser, password=xpw, dbname=xdbname, host=xdbhost, port=xdbport, unix.sock=xdbsock)


xbool_tableExists <- dbExistsTable(con, "nba_players_1") ; xbool_tableExists


```




```{r runQueryA, echo=FALSE, eval=TRUE, results='hide'}

##### get min and max date

qstr <- "SELECT MIN(date), MAX(date) FROM nba_playersDate_1"

xx <- dbGetQuery(con, qstr)
xx

xMinDataDate <- xx[1, 1]
xMaxDataDate <- xx[1, 2]

xminDD <- format( strptime(xMinDataDate, "%Y%m%d"), "%Y-%m-%d")
xmaxDD <- format( strptime(xMaxDataDate, "%Y%m%d"), "%Y-%m-%d")

```


NBA data from `r xminDD` to `r xmaxDD`.




```{r runQueryB, echo=FALSE, eval=TRUE, results='hide'}

xptotpnts <- 50

qstr <- paste0("SELECT date, name, team, pts FROM nba_playersDate_1 WHERE pts > ", xptotpnts)
xx <- dbGetQuery(con, qstr)
#xx


```


<style type="text/css">
.table {
    width: 40%;
}
</style>

Here is a table all all the occurrences of a player in our data scoring more than `r xptotpnts` points in a game:

```{r runQueryC, echo=FALSE, eval=TRUE, results='show', table.width='5cm'}

kable(xx)

```

### References




