

---
title: "Officials in NHL Games with Prolific Player Scoring"
geometry: 'left=12mm, right=12mm, top=15mm, bottom=15mm'
fontsize: 12pt
output:
  html_document:
    theme: paper
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    latex_engine: xelatex
    keep_tex:  true
    toc: no
    toc_depth: '3'
header-includes:
 \usepackage{fontspec}
 \usepackage{background}
 \usepackage{float}
 \backgroundsetup{
 scale=1,
 color=black,
 opacity=0.15,
 angle=0,
 pages=all,
 contents={\includegraphics[width=16.5cm,height=40cm]{nhl_action_01.jpg}}
 }
 \setmainfont{Avenir} 
 
---



<style type="text/css">.main-container {  max-width: 2800px;  margin-left: auto;  margin-right: auto;}</style>

```{r NOTES, echo=FALSE, eval=FALSE, results='hide'}

#### if this doesn't build, try removing lines in header above
####  \usepackage{fontspec}
####  \setmainfont{Avenir} 

#### You can also try installing R library tinytex
#### On Mac, you can see a list of available fonts issuing this command in Terminal:
#### fc-list :outline -f "%{family}\n" 

```



```{r datetime, echo=FALSE, eval=TRUE}

xtoday <-  format(Sys.time(), "%Y-%m-%d")

#cat("Date last run:", xtoday)
#cat("\n")
#cat("Stats MAS405 Spring 2020")
#cat("\n")
## cat("Section #")

options(width=200, xtable.comment = FALSE)


###### we can use this to get current build output
###### useful when deciding how to format tables


```

`r xtoday`

Stats MAS405 Spring 2021

your names







```{r TOP, echo=FALSE, message=FALSE, eval=TRUE, results='hide'}

#### note ``` (3 backticks)
##### R code goes in here.  Set code chunk environment options above



projpath <- getwd()

if(!exists("xdbsock")) {
    xdbsock <- ""
    cat("\n", "Parameter 'xdbsock' not found, setting to empty string for general usage", "\n")
}


library(RMySQL)
library(knitr)
library(xtable)

### opts_knit$get("rmarkdown.pandoc.to")


drv <- dbDriver("MySQL")




xdbuser <- Sys.getenv("MAS405_AWS_DZES_DB_RO_USER") ### 
xpw     <- Sys.getenv("MAS405_AWS_DZES_DB_RO_PW") ### 
xdbname <- Sys.getenv("MAS405_AWS_DZES_DB_RO_DBNAME") ### 
xdbhost <- Sys.getenv("MAS405_AWS_DZES_DB_RO_HOST") ###
xdbport <- as.integer( Sys.getenv("MAS405_AWS_DZES_DB_RO_PORT") )


############# db1
#xdbuser <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_USER")
#dzpw <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_PW")
#xdbname <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_DBNAME")
#xdbhost <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_HOST")
#xdbport <- as.integer( Sys.getenv("MAS405_AWS_MY_DB_ADMIN_PORT") )




con <- dbConnect(drv, user=xdbuser, password=xpw, dbname=xdbname, host=xdbhost, port=xdbport, unix.sock=xdbsock)


```


```{r runQueryDate, echo=FALSE, eval=TRUE, results='hide'}

##### get min and max date

qstr <- "SELECT MIN(date), MAX(date) FROM nhl_playersDate_1"

xx <- dbGetQuery(con, qstr)
xx

xMinDataDate <- xx[1, 1]
xMaxDataDate <- xx[1, 2]

xminDD <- format( strptime(xMinDataDate, "%Y%m%d"), "%Y-%m-%d")
xmaxDD <- format( strptime(xMaxDataDate, "%Y%m%d"), "%Y-%m-%d")

xpntsCO <- 3

```


## Introduction

<!--
%In the NBA, are some officials more likely than others to have officiated a game in which a player had proliffic scoring?
-->
In the NHL, are some officials more likely than others to have officiated a game with a prolific individual player performance?
Utilizing regular season NHL game and player data spanning `r xminDD` to `r xmaxDD`, we produce frequencies of officials in games where a player scored `r xpntsCO+1` or more goals.











