---
output:
  pdf_document: default
  html_document: default
---


## R Markdown Skeleton



---
title: "EXAMPLE"
output:
  pdf_document:
    toc: yes
    toc_depth: '3'
  html_document:
    theme: paper
    toc: yes
    toc_depth: 3
    toc_float: yes
---






```{r TOP, echo=TRUE, message=FALSE, eval=TRUE, results='hide'}

#### note ``` (3 backticks)
##### R code goes in here.  Set code chunk environment options above

library(RMySQL)
library(knitr)
library(xtable)

options(xtable.comment = FALSE) #### prevent comment when printing xtable latex

projpath <- getwd()

if(!exists("xdbsock")) {
    xdbsock <- ""
    cat("\n", "Parameter 'xdbsock' not found, setting to empty string for general usage", "\n")
}





drv <- dbDriver("MySQL")




xdbuser <- Sys.getenv("MAS405_AWS_DZES_DB_RO_USER") ### 
xpw     <- Sys.getenv("MAS405_AWS_DZES_DB_RO_PW") ### 
xdbname <- Sys.getenv("MAS405_AWS_DZES_DB_RO_DBNAME") ### 
xdbhost <- Sys.getenv("MAS405_AWS_DZES_DB_RO_HOST") ###
xdbport <- as.integer( Sys.getenv("MAS405_AWS_DZES_DB_RO_PORT") )

con <- dbConnect(drv, user=xdbuser, password=xpw, dbname=xdbname, host=xdbhost, port=xdbport, unix.sock=xdbsock)




xbool_tableExists <- dbExistsTable(con, "nba_playersDate_1") ; xbool_tableExists




```


Document environment.  Accepts text like this


<p style='font-family:Verdana;'> Accepts HTML/CSS </p>


and LaTeX equations: $y=b_0 + b_1 x$


You can also take a result from a previous R environment and display it inline, like so, `r xbool_tableExists`.


# NBA Players-Game Data

## H2

### H3

#### H4




```{r datetime, echo=FALSE, eval=TRUE}

###### we can use this to get current build output
###### useful when deciding how to format tables
opts_knit$get("rmarkdown.pandoc.to")

cat("Date last run:", format(Sys.time(), "%Y-%m-%d"))
cat("\n")
cat("Stats 10 Winter 2020")
cat("\n")
cat("Section #")

options(width=90)

```




## Show All Tables in DB db3

```{r runQueryTables, echo=FALSE, eval=TRUE, results='show'}

##### get min and max date

qstr <- "SHOW TABLES"

xx <- dbGetQuery(con, qstr)
#xx

## kable(xx)



```

```{r runQueryTablesPrint, echo=TRUE, eval=TRUE, results='asis'}

##### we can use opts_knit$get("rmarkdown.pandoc.to") to determine whether we'd 
##### rather use kable or xtable to render a table 

if( opts_knit$get("rmarkdown.pandoc.to") %in% "html" ) {
  kable(xx)
}

if( opts_knit$get("rmarkdown.pandoc.to") %in% "latex" ) {
  print(xtable(xx))
}



```


## Column Info on Table nba_players_1

```{r runQueryInfo, echo=FALSE, eval=TRUE, results='show'}

##### get min and max date

qstr <- "SELECT COLUMN_NAME FROM INFORMATION_SCHEMA.COLUMNS WHERE TABLE_NAME='nba_playersDate_1'"

xx <- dbGetQuery(con, qstr)
#xx

kable(xx)

```






```{r runQueryA, echo=FALSE, eval=TRUE, results='hide'}

##### get min and max date

qstr <- "SELECT MIN(date), MAX(date) FROM nba_playersDate_1"

xx <- dbGetQuery(con, qstr)
xx

xMinDataDate <- xx[1, 1]
xMaxDataDate <- xx[1, 2]

xminDD <- format( strptime(xMinDataDate, "%Y%m%d"), "%Y-%m-%d")
xmaxDD <- format( strptime(xMaxDataDate, "%Y%m%d"), "%Y-%m-%d")

```





Earliest date in NBA Players data is, `r xMinDataDate`; most recent is `r xMaxDataDate`.


Earliest date, ISO, in NBA Players data is, `r xminDD`; most recent is `r xmaxDD`.



## Player-Game Points

```{r runQueryB, echo=FALSE, eval=TRUE, results='show', fig.width=6}

##### get min and max date

qstr <- "SELECT pts FROM nba_playersDate_1"

xx <- dbGetQuery(con, qstr)
#xx

pts <- xx[, 1]


hist(pts)


```


\newpage

## All Player-Game Where Player Pts > 60

```{r runQueryPlayer50Pts, echo=FALSE, eval=TRUE, results='show', fig.width=6}

##### get min and max date

qstr <- paste0("SELECT date, name, team FROM nba_playersDate_1 WHERE pts > 60")
xx <- dbGetQuery(con, qstr)
#xx

kable(xx)


```





