

---
title: "Officials in NBA Games with Prolific Player Scoring"
geometry: 'left=12mm, right=12mm, top=15mm, bottom=15mm'
fontsize: 12pt
output:
  html_document:
    theme: paper
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    latex_engine: xelatex
    keep_tex:  true
    toc: no
    toc_depth: '3'
header-includes:
 \usepackage{fontspec}
 \usepackage{background}
 \usepackage{float}
 \backgroundsetup{
 scale=1,
 color=black,
 opacity=0.20,
 angle=0,
 pages=all,
 contents={\includegraphics[width=25cm,height=40cm]{nba_action_02.jpg}}
 }
 \setmainfont{Avenir} 
 
---



<style type="text/css">.main-container {  max-width: 2800px;  margin-left: auto;  margin-right: auto;}</style>

```{r NOTES, echo=FALSE, eval=FALSE, results='hide'}

#### if this doesn't build, try removing lines in header above
####  \usepackage{fontspec}
####  \setmainfont{Avenir} 

#### You can also try installing R library tinytex
#### On Mac, you can see a list of available fonts issuing this command in Terminal:
#### fc-list :outline -f "%{family}\n" 

```



```{r datetime, echo=FALSE, eval=TRUE}

xtoday <-  format(Sys.time(), "%Y-%m-%d")

#cat("Date last run:", xtoday)
#cat("\n")
#cat("Stats MAS405 Spring 2020")
#cat("\n")
## cat("Section #")

options(width=200, xtable.comment = FALSE)


###### we can use this to get current build output
###### useful when deciding how to format tables


```

`r xtoday`

Stats MAS405 Spring 2021

Dave Zes







```{r TOP, echo=FALSE, message=FALSE, eval=TRUE, results='hide'}

#### note ``` (3 backticks)
##### R code goes in here.  Set code chunk environment options above



projpath <- getwd()

if(!exists("xdbsock")) {
    xdbsock <- ""
    cat("\n", "Parameter 'xdbsock' not found, setting to empty string for general usage", "\n")
}


library(RMySQL)
library(knitr)
library(xtable)

### opts_knit$get("rmarkdown.pandoc.to")


drv <- dbDriver("MySQL")




xdbuser <- Sys.getenv("MAS405_AWS_DZES_DB_RO_USER") ### 
dzpw <- Sys.getenv("MAS405_AWS_DZES_DB_RO_PW") ### 
xdbname <- Sys.getenv("MAS405_AWS_DZES_DB_RO_DBNAME") ### 
xdbhost <- Sys.getenv("MAS405_AWS_DZES_DB_RO_HOST") ###
xdbport <- as.integer( Sys.getenv("MAS405_AWS_DZES_DB_RO_PORT") )


############# db1
#xdbuser <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_USER")
#dzpw <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_PW")
#xdbname <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_DBNAME")
#xdbhost <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_HOST")
#xdbport <- as.integer( Sys.getenv("MAS405_AWS_MY_DB_ADMIN_PORT") )




con <- dbConnect(drv, user=xdbuser, password=dzpw, dbname=xdbname, host=xdbhost, port=xdbport, unix.sock=xdbsock)


```


```{r runQueryDate, echo=FALSE, eval=TRUE, results='hide'}

##### get min and max date

qstr <- "SELECT MIN(date), MAX(date) FROM nba_playersDate_1"

xx <- dbGetQuery(con, qstr)
xx

xMinDataDate <- xx[1, 1]
xMaxDataDate <- xx[1, 2]

xminDD <- format( strptime(xMinDataDate, "%Y%m%d"), "%Y-%m-%d")
xmaxDD <- format( strptime(xMaxDataDate, "%Y%m%d"), "%Y-%m-%d")

xpntsCO <- 55

```


## Introduction

<!--
%In the NBA, are some officials more likely than others to have officiated a game in which a player had proliffic scoring?
-->
In the NBA, are some officials more likely than others to have officiated a game with a prolific individual player performance?
Utilizing regular season NBA game and player data spanning `r xminDD` to `r xmaxDD`, we produce frequencies of officials in games where a player scored more than `r xpntsCO` points.







```{r runQuery1, echo=FALSE, eval=TRUE, results='hide'}

qstr <-
paste0(
"SELECT * FROM nba_gameDate_1  ",
"JOIN nba_playersDate_1 ON (nba_gameDate_1.date=nba_playersDate_1.date AND nba_gameDate_1.VT=nba_playersDate_1.team)  ",
" OR (nba_gameDate_1.date=nba_playersDate_1.date AND nba_gameDate_1.HT=nba_playersDate_1.team)  ",
"WHERE nba_playersDate_1.pts > ", xpntsCO
)
qstr
xx <- dbGetQuery(con, qstr)
xx

df_out <- xx

class(df_out)

colnames(df_out) ##### non-unique column names!


colnames(df_out) <- make.names(names=colnames(df_out), unique = TRUE)

df_out


df_out_sub <- df_out[ , c("date", "VT", "HT", "min", "refs", "team", "name", "min.1", "pts")]

nHSgames <- nrow(df_out_sub)

library(kableExtra)

```


<style type="text/css">
#resultsT1 {
  width: 140% ;
}
#resultsOfficials1 {
  width: 50% ;
}
</style>


## Results

Table 1 shows game information for all games in our data where a player (name) scored more than `r xpntsCO` points.


```{r runQuery1result, echo=FALSE, eval=TRUE, results='asis', table.width=20}

### kable(df_out_sub, format="html", table.attr = "style='width:40% ;'")

##### we can use opts_knit$get("rmarkdown.pandoc.to") to determine whether we'd 
##### rather use kable or xtable to render a table 

if( opts_knit$get("rmarkdown.pandoc.to") %in% "html" ) {
  kable(df_out_sub, format="html", table.attr = "style='width:100% ;'")
}

if( opts_knit$get("rmarkdown.pandoc.to") %in% "latex" ) {
  
  xcaption <- "NBA games in data where player scored more than 55 points."
  

  #xxtb <- kable(df_out_sub, format="latex", caption=xcaption)
  #kable_styling(xxtb, latex_options=c("scale_down", "HOLD_position", "striped") )
  

  x.big <- suppressWarnings(xtable(df_out_sub, label='tabbig'))

  caption(x.big) <- xcaption

  ## xx <- suppressWarnings(print(x.big, tabular.environment='longtable', include.rownames=FALSE, print.results=FALSE))

  xx <- 
    suppressWarnings(
    print(
      x.big, 
      tabular.environment='tabular', 
      include.rownames=FALSE, 
      print.results=FALSE
      )
    )
  
  #print(x.big, tabular.environment='longtable',
  #      floating=FALSE,include.rownames=FALSE, 
  #      hline.after = c(-1,nrow(x.big)),
  #      add.to.row = list(pos = list(0),
  #      command = "\\hline \\endhead "), file = "output.tex")
  yy <- strsplit(xx, "\n")[[1]]
  
  yy <- c(yy[1], "\\scriptsize", yy[2:length(yy)])
  
  writeLines(yy, "output.tex")
  
}



```


\input{output.tex}


\newpage

<!--
#### Frequency of Officials

Table 1 shows game information for all games in our data where a player (name) scored more than `r xpntsCO` points.
-->

```{r runOfficials, echo=FALSE, eval=TRUE, results='show'}

xofficials <- gsub("^\\s*|\\s*$", "", (unlist(strsplit(df_out_sub[ , "refs"], ","))))

xoff_df <- as.data.frame(table(xofficials))

xoff_df <- xoff_df[ order(xoff_df[ , "Freq"], decreasing=TRUE), ]



```


```{r runTableOfficials, echo=FALSE, eval=TRUE, results='asis'}


if( opts_knit$get("rmarkdown.pandoc.to") %in% "html" ) {
  #kable( xoff_df, format="html", table.attr = "id=\"resultsOfficials1\""  )
  
  nuoffs <- nrow(xoff_df)
  
  xxtb <- kable( xoff_df, format="html", table.attr = "style='width:40% ;'"  )
  xxtb
  #kable_styling(xxtb)
}

if( opts_knit$get("rmarkdown.pandoc.to") %in% "latex" ) {

  
  nuoffs <- nrow(xoff_df)
  
  #xxtb <- kable(xoff_df, format="latex")

  #kable_styling(xxtb, latex_options="repeat_header", latex_table_env="longtable", repeat_header_text = "\\textit{(continued)}", repeat_header_continued = TRUE)
  
  ###### "{ }\\" -- try to create some vertical space
  xcaption2 <- paste0("{ }\\\\Frequency of officials who have officiated games where a player scored more than ", xpntsCO, " points (see Table 1)")
  
  colnames(xoff_df) <- c("official", "numGames")
  
  x.big <- suppressWarnings(xtable(xoff_df))

  caption(x.big) <-  xcaption2

  ## xx <- suppressWarnings(print(x.big, tabular.environment='longtable', include.rownames=FALSE, print.results=FALSE))

  xx <- 
    suppressWarnings(
      print(
        x.big, 
        size='\\fontsize{7pt}{7pt}\\selectfont',
        tabular.environment='longtable', 
        include.rownames=FALSE, 
        print.results=FALSE
        )
      )
  

  #yy <- strsplit(xx, "\n")[[1]]
  
  #yy <- c(yy[1], "\\tiny", yy[2:length(yy)])
  yy <- xx
  
  writeLines(yy, "output_2.tex")

  
  
}

```

\input{output_2.tex}




Table 2: `r nuoffs` unique officials have officiated the `r nHSgames` games in our data in which a player scored more than `r xpntsCO` (see Table 1).  Of these, Eric Lewis has officiated the most, with 4. 




```{r ericLewis, echo=FALSE, eval=TRUE, results='hide'}


xndx <- which(grepl('Eric Lewis', df_out_sub[ , 'refs']))

df_EL <- df_out_sub[ xndx, c('date', 'VT', 'HT', 'name', 'pts') ]


```




```{r runTableLewis, echo=FALSE, eval=TRUE, results='asis'}


if( opts_knit$get("rmarkdown.pandoc.to") %in% "html" ) {
  xxtb <- kable( df_EL, format="html", table.attr = "style='width:40% ;'"  )
  xxtb
  #kable_styling(xxtb)
}

if( opts_knit$get("rmarkdown.pandoc.to") %in% "latex" ) {

 
  ###### "{ }\\" -- try to create some vertical space
  xcaption3 <- paste0("{ }\\Frequency of officials who have officiated games where a player scored more than ", xpntsCO, " points (see Table 1)")
  xcaption3 <- paste0("High Player Scoring games in which Eric Lewis officiated.")
  
  x.big <- suppressWarnings(xtable(df_EL))

  caption(x.big) <-  xcaption3

  ## xx <- suppressWarnings(print(x.big, tabular.environment='longtable', include.rownames=FALSE, print.results=FALSE))

  xx <- 
    suppressWarnings(
      print(
        x.big, 
        #size='\\fontsize{10pt}{10pt}\\selectfont',
        tabular.environment='tabular', 
        include.rownames=FALSE, 
        print.results=FALSE
        )
      )
  

  #yy <- strsplit(xx, "\n")[[1]]
  
  #yy <- c(yy[1], "\\tiny", yy[2:length(yy)])
  yy <- xx
  
  writeLines(yy, "output_3.tex")

}

```



\input{output_3.tex}









